Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-09 documentation/paper.tex
Added subscripts to betas
Explained wall cuts more clearly

Except where specifically mentioned, $WallCut(D)$ was not applied. This was done to test the network's ability to handle complex acoustic characteristics including resonance. There is a relatively clear-cut discrimination boundary in PICO-60, but this may not be the case in other applications.

@@

\begin{tabular}{|l|l|l|}
    \hline
    Configuration & Max Accuracy & Mean Class-Wise Standard Deviation \\
    \hline
    $FourierMLP(PosCor(\beta{8}), \chi)$ & 97\% & 0.42 \\
    \hline
    $FourierMLP(\beta{8})$ & 98\% & 0.29 \\
    \hline
    $FourierMLPWithPos(\beta{8}, \chi)$ & 95\% & 0.44 \\
    \hline
    $FourierMLPWithPos(\beta{20}, \chi)$ & 94\% & 0.52 \\
    \hline
    $FourierMLPWithPos(\beta{40}, \chi)$ & 91\% & 0.54 \\
    \hline
    Original PICO-60 Neural Network & 94\% & 0.99 \\
    \hline
    Acoustic Parameter & N/A & 0.56 \\
    \hline
\end{tabular}

@@

\begin{tabular}{|l|l|l|}
    \hline
    Configuration & Max Accuracy & Mean Class-Wise Standard Deviation \\
    \hline
    $FourierMLPWithPos(\beta_{20}, \chi)$ & 92\% & 0.63 \\
    \hline
    $FourierMLPWithPos(\beta{50,001}, \chi)$ & 97\% & 0.47 \\
    \hline
    $DeepConv(\omega)$ & 77\% & 0.86 \\
    \hline
    $DeepConvWithPos(\omega, \chi)$ & 91\% & 0.61 \\
    \hline
    $ImageConv(\iota)$ & 85\% & 0.95 \\
    \hline
    Acoustic Parameter & N/A & 0.73 \\
    \hline
\end{tabular}

>>>>

Except where specifically mentioned, $WallCut(D)$ was not applied. This was done for 2 reasons:

\begin{enumerate}
    \item As an exploratory effort, to determine whether or not it was possible to produce an effective discriminator without wall cuts. No such thing was attempted during the original PICO-60 analysis.
    \item To test the network's ability to handle complex acoustic characteristics including resonance. There is a relatively clear-cut discrimination boundary in PICO-60, but this may not be the case in other applications.
\end{enumerate}

@@

\begin{tabular}{|l|l|l|}
    \hline
    Configuration & Max Accuracy & Mean Class-Wise Standard Deviation \\
    \hline
    $FourierMLP(PosCor(\beta_{8}), \chi)$ & 97\% & 0.42 \\
    \hline
    $FourierMLP(\beta_{8})$ & 98\% & 0.29 \\
    \hline
    $FourierMLPWithPos(\beta_{8}, \chi)$ & 95\% & 0.44 \\
    \hline
    $FourierMLPWithPos(\beta_{20}, \chi)$ & 94\% & 0.52 \\
    \hline
    $FourierMLPWithPos(\beta_{40}, \chi)$ & 91\% & 0.54 \\
    \hline
    Original PICO-60 Neural Network & 94\% & 0.99 \\
    \hline
    Acoustic Parameter & N/A & 0.56 \\
    \hline
\end{tabular}

@@

\begin{tabular}{|l|l|l|}
    \hline
    Configuration & Max Accuracy & Mean Class-Wise Standard Deviation \\
    \hline
    $FourierMLPWithPos(\beta_{20}, \chi)$ & 92\% & 0.63 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 97\% & 0.47 \\
    \hline
    $DeepConv(\omega)$ & 77\% & 0.86 \\
    \hline
    $DeepConvWithPos(\omega, \chi)$ & 91\% & 0.61 \\
    \hline
    $ImageConv(\iota)$ & 85\% & 0.95 \\
    \hline
    Acoustic Parameter & N/A & 0.73 \\
    \hline
\end{tabular}
